Assessing United States county-level exposure for tropical cyclone impact research

### 2020-09-09 ehp_revision/response_to_reviewers.Rmd

---
title: "Response to reviewers' comments for *\"Assessing United States county-level exposure for research on tropical cyclones and human health\"*"
output: bookdown::pdf_document2
toc: false
bibliography: writing/hurr_exposure.bib
header-includes:
- \usepackage{xcolor}
- \usepackage{framed}
- \usepackage{bm}
- \usepackage{subcaption}
- \usepackage{gensymb}
- \renewcommand\familydefault{\sfdefault}
- \usepackage{sansmath}
- \usepackage{bm}
- \usepackage{soul}
- \sansmath
- \usepackage{booktabs}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{pdflscape}
- \usepackage{float}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{fullpage}
- \usepackage{pdflscape}
- \usepackage{tcolorbox}
- \tcbuselibrary{skins,breakable}
- \usepackage{amsmath}
- \usepackage{xtab}
- \usepackage{rotating}
- \allowdisplaybreaks
- \usepackage[nomarkers]{endfloat}
- \pagenumbering{gobble}
- \newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
---

@@

\medskip

\begin{shaded}
\textbf{EHP Request 5:}
Figures 5--6: Please check to see if the colors used can be distinguished if
printed in black and white, and if not, use a “color-blind friendly” palette if
possible. If this is not feasible, we can request and exemption from
accessibility requirements, but we try to do this only when alternatives  would
degrade the information content of  the figure.
\end{shaded}

**Response:**

As we note in our response to EHP Request 2, we used colormaps for all figures
that are designed to be perceptible both for those with common types of color
vision deficiency and when printed in grayscale Figures \@ref(fig:fig5check1)
and \@ref(fig:fig5check2) show what Figure 5 of the main text would look like
under three common types of color vision deficiency and when printed in black
and white. Figures \@ref(fig:fig6check1) and \@ref(fig:fig6check2) show the same
thing for Figure 6 of the main text. Therefore, these figures should not require
any exemption from accessibility requirements, as they should satisfy these
requirements.

### 2020-09-09 ehp_revision/tables/flood_misclass.tex
Work some more on revisions
Work more on revision

% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Thu Sep  3 12:19:54 2020
\begin{table}[ht]
\centering
\caption{Caption. Limited to storms with at least 250 counties assessed as exposed based on at least one exposure metric considered in this study. Numbers are out of 2,396 counties in the study area (states in the eastern half of the US). Exposure assessment is based on the thresholds given in Table 1 of the main text. The Jaccard index shown in Figure [x] of the main text is based on numbers in the second through fourth columns (the value in the second column divide by the sum of numbers in the second through fourth columns). Storms are ordered based on the number of counties exposed to at least one of these two exposure metrics.} 
\begin{tabular}{cp{3cm}p{3cm}p{3cm}p{3cm}}
  \toprule
Storm & Exposed for both distance metric and flood metric & Exposed for distance metric but unexposed for flood metric & Exposed for flood metric but unexposed for distance metric & Unexposed for both distance metric and flood metric \\ 
  \midrule
Ivan (2004) & 79 & 205 & 238 & 1,874 \\ 
  Frances (2004) & 103 & 218 & 122 & 1,953 \\ 
  Dennis (2005) & 21 & 271 & 87 & 2,017 \\ 
  Jeanne (2004) & 80 & 217 & 77 & 2,022 \\ 
  Allison (2001) & 68 & 219 & 71 & 2,038 \\ 
  Cindy (2005) & 52 & 269 & 29 & 2,046 \\ 
  Ike (2008) & 48 & 185 & 101 & 2,062 \\ 
  Isidore (2002) & 30 & 238 & 64 & 2,064 \\ 
  Fay (2008) & 23 & 229 & 60 & 2,084 \\ 
  Bill (2003) & 39 & 191 & 65 & 2,101 \\ 
  Gustav (2008) & 36 & 198 & 57 & 2,105 \\ 
  Katrina (2005) & 47 & 194 & 47 & 2,108 \\ 
  Gordon (2000) & 7 & 248 & 19 & 2,122 \\ 
  Arlene (2005) & 11 & 225 & 29 & 2,131 \\ 
  Danny (1997) & 39 & 190 & 31 & 2,136 \\ 
  Floyd (1999) & 100 & 39 & 120 & 2,137 \\ 
  Fran (1996) & 46 & 105 & 77 & 2,168 \\ 
  Dennis (1999) & 38 & 162 & 19 & 2,177 \\ 
  Ernesto (2006) & 44 & 148 & 27 & 2,177 \\ 
  Bertha (1996) & 27 & 156 & 17 & 2,196 \\ 
  Rita (2005) & 4 & 161 & 26 & 2,205 \\ 
  Lee (2011) & 18 & 126 & 36 & 2,216 \\ 
   \bottomrule
\end{tabular}
\end{table}

>>>>

% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Wed Sep  9 17:22:05 2020
\begin{table}[ht]
\centering
\caption{Caption. Limited to storms with at least 200 counties assessed as exposed based on at least one exposure metric considered in this study. Numbers are out of 2,396 counties in the study area (states in the eastern half of the US). Exposure assessment is based on the thresholds given in Table 1 of the main text. The Jaccard index shown in Figure 7 of the main text is based on numbers in the second through fourth columns (the value in the second column divide by the sum of numbers in the second through fourth columns). Storms are ordered based on the number of counties exposed to at least one of these two exposure metrics.} 
\label{tab:misclassflood}
\begin{tabular}{cP{3cm}P{3cm}P{3cm}P{3cm}}
  \toprule
Storm & Exposed for both distance metric and flood metric & Exposed for distance metric but unexposed for flood metric & Exposed for flood metric but unexposed for distance metric & Unexposed for both distance metric and flood metric \\ 
  \midrule
Ivan (2004) & 79 & 205 & 238 & 1,874 \\ 
  Frances (2004) & 103 & 218 & 122 & 1,953 \\ 
  Dennis (2005) & 21 & 271 & 87 & 2,017 \\ 
  Jeanne (2004) & 80 & 217 & 77 & 2,022 \\ 
  Allison (2001) & 68 & 219 & 71 & 2,038 \\ 
  Cindy (2005) & 52 & 269 & 29 & 2,046 \\ 
  Ike (2008) & 48 & 185 & 101 & 2,062 \\ 
  Isidore (2002) & 30 & 238 & 64 & 2,064 \\ 
  Fay (2008) & 23 & 229 & 60 & 2,084 \\ 
  Bill (2003) & 39 & 191 & 65 & 2,101 \\ 
  Gustav (2008) & 36 & 198 & 57 & 2,105 \\ 
  Katrina (2005) & 47 & 194 & 47 & 2,108 \\ 
  Gordon (2000) & 7 & 248 & 19 & 2,122 \\ 
  Arlene (2005) & 11 & 225 & 29 & 2,131 \\ 
  Danny (1997) & 39 & 190 & 31 & 2,136 \\ 
  Floyd (1999) & 100 & 39 & 120 & 2,137 \\ 
  Fran (1996) & 46 & 105 & 77 & 2,168 \\ 
  Dennis (1999) & 38 & 162 & 19 & 2,177 \\ 
  Ernesto (2006) & 44 & 148 & 27 & 2,177 \\ 
  Hanna (2008) & 52 & 140 & 26 & 2,178 \\ 
  Helene (2000) & 13 & 179 & 20 & 2,184 \\ 
  Bertha (1996) & 27 & 156 & 17 & 2,196 \\ 
  Irene (2011) & 108 & 12 & 79 & 2,197 \\ 
  Rita (2005) & 4 & 161 & 26 & 2,205 \\ 
  Earl (1998) & 4 & 165 & 11 & 2,216 \\ 
  Lee (2011) & 18 & 126 & 36 & 2,216 \\ 
  Hermine (2010) & 16 & 107 & 40 & 2,233 \\ 
  Isabel (2003) & 39 & 108 & 9 & 2,240 \\ 
  Josephine (1996) & 27 & 96 & 32 & 2,241 \\ 
  Bonnie (2004) & 10 & 99 & 29 & 2,258 \\ 
  Frances (1998) & 8 & 54 & 23 & 2,311 \\ 
   \bottomrule
\end{tabular}
\end{table}

### 2020-09-09 ehp_revision/tables/rain_misclass.tex
Work some more on revisions
Work more on revision

% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Thu Sep  3 12:19:54 2020
\begin{table}[ht]
\centering
\caption{Caption. Limited to storms with at least 250 counties assessed as exposed based on at least one exposure metric considered in this study. Numbers are out of 2,396 counties in the study area (states in the eastern half of the US). Exposure assessment is based on the thresholds given in Table 1 of the main text. The Jaccard index shown in Figure [x] of the main text is based on numbers in the second through fourth columns (the value in the second column divide by the sum of numbers in the second through fourth columns.  Storms are ordered based on the number of counties exposed to at least one of these two exposure metrics.).} 
\begin{tabular}{cp{3cm}p{3cm}p{3cm}p{3cm}}
  \toprule
Storm & Exposed for both distance metric and rain metric & Exposed for distance metric but unexposed for rain metric & Exposed for rain metric but unexposed for distance metric & Unexposed for both distance metric and rain metric \\ 
  \midrule
Frances (2004) & 207 & 114 & 257 & 1,818 \\ 
  Ivan (2004) & 124 & 160 & 288 & 1,824 \\ 
  Isidore (2002) & 134 & 134 & 186 & 1,942 \\ 
  Ike (2008) & 113 & 120 & 213 & 1,950 \\ 
  Dennis (2005) & 48 & 244 & 124 & 1,980 \\ 
  Fay (2008) & 72 & 180 & 163 & 1,981 \\ 
  Jeanne (2004) & 144 & 153 & 113 & 1,986 \\ 
  Lee (2011) & 106 & 38 & 230 & 2,022 \\ 
  Gustav (2008) & 126 & 108 & 137 & 2,025 \\ 
  Allison (2001) & 106 & 181 & 67 & 2,042 \\ 
  Bill (2003) & 110 & 120 & 117 & 2,049 \\ 
  Cindy (2005) & 78 & 243 & 11 & 2,064 \\ 
  Floyd (1999) & 129 & 10 & 170 & 2,087 \\ 
  Katrina (2005) & 195 & 46 & 58 & 2,097 \\ 
  Danny (1997) & 82 & 147 & 54 & 2,113 \\ 
  Rita (2005) & 64 & 101 & 103 & 2,128 \\ 
  Gordon (2000) & 5 & 250 & 7 & 2,134 \\ 
  Arlene (2005) & 39 & 197 & 23 & 2,137 \\ 
  Dennis (1999) & 90 & 110 & 56 & 2,140 \\ 
  Ernesto (2006) & 124 & 68 & 63 & 2,141 \\ 
  Fran (1996) & 89 & 62 & 73 & 2,172 \\ 
  Bertha (1996) & 103 & 80 & 20 & 2,193 \\ 
   \bottomrule
\end{tabular}
\end{table}

>>>>

% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Wed Sep  9 17:22:05 2020
\begin{table}[ht]
\centering
\caption{Caption. Limited to storms with at least 200 counties assessed as exposed based on at least one exposure metric considered in this study. Numbers are out of 2,396 counties in the study area (states in the eastern half of the US). Exposure assessment is based on the thresholds given in Table 1 of the main text. The Jaccard index shown in Figure 7 of the main text is based on numbers in the second through fourth columns (the value in the second column divide by the sum of numbers in the second through fourth columns.  Storms are ordered based on the number of counties exposed to at least one of these two exposure metrics.).} 
\label{tab:misclassrain}
\begin{tabular}{cP{3cm}P{3cm}P{3cm}P{3cm}}
  \toprule
Storm & Exposed for both distance metric and rain metric & Exposed for distance metric but unexposed for rain metric & Exposed for rain metric but unexposed for distance metric & Unexposed for both distance metric and rain metric \\ 
  \midrule
Frances (2004) & 207 & 114 & 257 & 1,818 \\ 
  Ivan (2004) & 124 & 160 & 288 & 1,824 \\ 
  Isidore (2002) & 134 & 134 & 186 & 1,942 \\ 
  Ike (2008) & 113 & 120 & 213 & 1,950 \\ 
  Dennis (2005) & 48 & 244 & 124 & 1,980 \\ 
  Fay (2008) & 72 & 180 & 163 & 1,981 \\ 
  Jeanne (2004) & 144 & 153 & 113 & 1,986 \\ 
  Lee (2011) & 106 & 38 & 230 & 2,022 \\ 
  Gustav (2008) & 126 & 108 & 137 & 2,025 \\ 
  Allison (2001) & 106 & 181 & 67 & 2,042 \\ 
  Bill (2003) & 110 & 120 & 117 & 2,049 \\ 
  Cindy (2005) & 78 & 243 & 11 & 2,064 \\ 
  Floyd (1999) & 129 & 10 & 170 & 2,087 \\ 
  Katrina (2005) & 195 & 46 & 58 & 2,097 \\ 
  Danny (1997) & 82 & 147 & 54 & 2,113 \\ 
  Rita (2005) & 64 & 101 & 103 & 2,128 \\ 
  Gordon (2000) & 5 & 250 & 7 & 2,134 \\ 
  Arlene (2005) & 39 & 197 & 23 & 2,137 \\ 
  Dennis (1999) & 90 & 110 & 56 & 2,140 \\ 
  Ernesto (2006) & 124 & 68 & 63 & 2,141 \\ 
  Irene (2011) & 119 & 1 & 106 & 2,170 \\ 
  Hanna (2008) & 100 & 92 & 33 & 2,171 \\ 
  Hermine (2010) & 44 & 79 & 102 & 2,171 \\ 
  Fran (1996) & 89 & 62 & 73 & 2,172 \\ 
  Earl (1998) & 72 & 97 & 38 & 2,189 \\ 
  Bertha (1996) & 103 & 80 & 20 & 2,193 \\ 
  Helene (2000) & 28 & 164 & 11 & 2,193 \\ 
  Frances (1998) & 27 & 35 & 139 & 2,195 \\ 
  Josephine (1996) & 94 & 29 & 77 & 2,196 \\ 
  Bonnie (2004) & 56 & 53 & 56 & 2,231 \\ 
  Isabel (2003) & 88 & 59 & 17 & 2,232 \\ 
   \bottomrule
\end{tabular}
\end{table}

### 2020-09-09 ehp_revision/tables/tornado_misclass.tex
Work some more on revisions
Work more on revision

% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Thu Sep  3 12:19:54 2020
\begin{table}[ht]
\centering
\caption{Caption. Limited to storms with at least 250 counties assessed as exposed based on at least one exposure metric considered in this study. Numbers are out of 2,396 counties in the study area (states in the eastern half of the US). Exposure assessment is based on the thresholds given in Table 1 of the main text. The Jaccard index shown in Figure [x] of the main text is based on numbers in the second through fourth columns (the value in the second column divide by the sum of numbers in the second through fourth columns). Storms are ordered based on the number of counties exposed to at least one of these two exposure metrics.} 
\begin{tabular}{cp{3cm}p{3cm}p{3cm}p{3cm}}
  \toprule
Storm & Exposed for both distance metric and tornado metric & Exposed for distance metric but unexposed for tornado metric & Exposed for tornado metric but unexposed for distance metric & Unexposed for both distance metric and tornado metric \\ 
  \midrule
Frances (2004) & 6 & 315 & 66 & 2,009 \\ 
  Ivan (2004) & 36 & 248 & 55 & 2,057 \\ 
  Cindy (2005) & 27 & 294 & 11 & 2,064 \\ 
  Jeanne (2004) & 13 & 284 & 22 & 2,077 \\ 
  Dennis (2005) & 0 & 292 & 6 & 2,098 \\ 
  Allison (2001) & 14 & 273 & 9 & 2,100 \\ 
  Katrina (2005) & 8 & 233 & 38 & 2,117 \\ 
  Fay (2008) & 15 & 237 & 26 & 2,118 \\ 
  Isidore (2002) & 1 & 267 & 6 & 2,122 \\ 
  Ike (2008) & 4 & 229 & 31 & 2,132 \\ 
  Gordon (2000) & 1 & 254 & 8 & 2,133 \\ 
  Gustav (2008) & 9 & 225 & 28 & 2,134 \\ 
  Bill (2003) & 4 & 226 & 22 & 2,144 \\ 
  Arlene (2005) & 2 & 234 & 7 & 2,153 \\ 
  Danny (1997) & 9 & 220 & 4 & 2,163 \\ 
  Rita (2005) & 8 & 157 & 41 & 2,190 \\ 
  Dennis (1999) & 0 & 200 & 1 & 2,195 \\ 
  Ernesto (2006) & 2 & 190 & 1 & 2,203 \\ 
  Bertha (1996) & 13 & 170 & 4 & 2,209 \\ 
  Fran (1996) & 1 & 150 & 4 & 2,241 \\ 
  Lee (2011) & 14 & 130 & 11 & 2,241 \\ 
  Floyd (1999) & 11 & 128 & 1 & 2,256 \\ 
   \bottomrule
\end{tabular}
\end{table}

>>>>

% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Wed Sep  9 17:22:05 2020
\begin{table}[ht]
\centering
\caption{Caption. Limited to storms with at least 200 counties assessed as exposed based on at least one exposure metric considered in this study. Numbers are out of 2,396 counties in the study area (states in the eastern half of the US). Exposure assessment is based on the thresholds given in Table 1 of the main text. The Jaccard index shown in Figure 7 of the main text is based on numbers in the second through fourth columns (the value in the second column divide by the sum of numbers in the second through fourth columns). Storms are ordered based on the number of counties exposed to at least one of these two exposure metrics.} 
\label{tab:misclasstornado}
\begin{tabular}{cP{3cm}P{3cm}P{3cm}P{3cm}}
  \toprule
Storm & Exposed for both distance metric and tornado metric & Exposed for distance metric but unexposed for tornado metric & Exposed for tornado metric but unexposed for distance metric & Unexposed for both distance metric and tornado metric \\ 
  \midrule
Frances (2004) & 6 & 315 & 66 & 2,009 \\ 
  Ivan (2004) & 36 & 248 & 55 & 2,057 \\ 
  Cindy (2005) & 27 & 294 & 11 & 2,064 \\ 
  Jeanne (2004) & 13 & 284 & 22 & 2,077 \\ 
  Dennis (2005) & 0 & 292 & 6 & 2,098 \\ 
  Allison (2001) & 14 & 273 & 9 & 2,100 \\ 
  Katrina (2005) & 8 & 233 & 38 & 2,117 \\ 
  Fay (2008) & 15 & 237 & 26 & 2,118 \\ 
  Isidore (2002) & 1 & 267 & 6 & 2,122 \\ 
  Ike (2008) & 4 & 229 & 31 & 2,132 \\ 
  Gordon (2000) & 1 & 254 & 8 & 2,133 \\ 
  Gustav (2008) & 9 & 225 & 28 & 2,134 \\ 
  Bill (2003) & 4 & 226 & 22 & 2,144 \\ 
  Arlene (2005) & 2 & 234 & 7 & 2,153 \\ 
  Danny (1997) & 9 & 220 & 4 & 2,163 \\ 
  Rita (2005) & 8 & 157 & 41 & 2,190 \\ 
  Dennis (1999) & 0 & 200 & 1 & 2,195 \\ 
  Helene (2000) & 5 & 187 & 6 & 2,198 \\ 
  Ernesto (2006) & 2 & 190 & 1 & 2,203 \\ 
  Hanna (2008) & 0 & 192 & 1 & 2,203 \\ 
  Bertha (1996) & 13 & 170 & 4 & 2,209 \\ 
  Earl (1998) & 8 & 161 & 7 & 2,220 \\ 
  Fran (1996) & 1 & 150 & 4 & 2,241 \\ 
  Lee (2011) & 14 & 130 & 11 & 2,241 \\ 
  Isabel (2003) & 0 & 147 & 1 & 2,248 \\ 
  Floyd (1999) & 11 & 128 & 1 & 2,256 \\ 
  Hermine (2010) & 1 & 122 & 12 & 2,261 \\ 
  Josephine (1996) & 7 & 116 & 12 & 2,261 \\ 
  Bonnie (2004) & 13 & 96 & 22 & 2,265 \\ 
  Irene (2011) & 9 & 111 & 0 & 2,276 \\ 
  Frances (1998) & 1 & 61 & 10 & 2,324 \\ 
   \bottomrule
\end{tabular}
\end{table}

### 2020-09-09 ehp_revision/tables/wind_misclass.tex
Work some more on revisions
Work more on revision

% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Thu Sep  3 12:19:54 2020
\begin{table}[ht]
\centering
\caption{Caption. Limited to storms with at least 250 counties assessed as exposed based on at least one exposure metric considered in this study. Numbers are out of 2,396 counties in the study area (states in the eastern half of the US). Exposure assessment is based on the thresholds given in Table 1 of the main text. The Jaccard index shown in Figure [x] of the main text is based on numbers in the second through fourth columns (the value in the second column divide by the sum of numbers in the second through fourth columns). Storms are ordered based on the number of counties exposed to at least one of these two exposure metrics.} 
\begin{tabular}{cp{3cm}p{3cm}p{3cm}p{3cm}}
  \toprule
Storm & Exposed for both distance metric and wind metric & Exposed for distance metric but unexposed for wind metric & Exposed for wind metric but unexposed for distance metric & Unexposed for both distance metric and wind metric \\ 
  \midrule
Frances (2004) & 44 & 277 & 13 & 2,062 \\ 
  Cindy (2005) & 17 & 304 & 4 & 2,071 \\ 
  Dennis (2005) & 18 & 274 & 26 & 2,078 \\ 
  Ike (2008) & 166 & 67 & 82 & 2,081 \\ 
  Ivan (2004) & 29 & 255 & 27 & 2,085 \\ 
  Jeanne (2004) & 41 & 256 & 7 & 2,092 \\ 
  Allison (2001) & 21 & 266 & 0 & 2,109 \\ 
  Isidore (2002) & 29 & 239 & 7 & 2,121 \\ 
  Katrina (2005) & 66 & 175 & 32 & 2,123 \\ 
  Gordon (2000) & 11 & 244 & 6 & 2,135 \\ 
  Fay (2008) & 54 & 198 & 7 & 2,137 \\ 
  Gustav (2008) & 36 & 198 & 23 & 2,139 \\ 
  Bertha (1996) & 179 & 4 & 62 & 2,151 \\ 
  Danny (1997) & 45 & 184 & 12 & 2,155 \\ 
  Arlene (2005) & 4 & 232 & 0 & 2,160 \\ 
  Bill (2003) & 19 & 211 & 0 & 2,166 \\ 
  Dennis (1999) & 17 & 183 & 13 & 2,183 \\ 
  Ernesto (2006) & 93 & 99 & 4 & 2,200 \\ 
  Rita (2005) & 26 & 139 & 20 & 2,211 \\ 
  Fran (1996) & 46 & 105 & 30 & 2,215 \\ 
  Floyd (1999) & 124 & 15 & 40 & 2,217 \\ 
  Lee (2011) & 34 & 110 & 0 & 2,252 \\ 
   \bottomrule
\end{tabular}
\end{table}

>>>>

% latex table generated in R 4.0.2 by xtable 1.8-4 package
% Wed Sep  9 17:22:05 2020
\begin{table}[ht]
\centering
\caption{Caption. Limited to storms with at least 200 counties assessed as exposed based on at least one exposure metric considered in this study. Numbers are out of 2,396 counties in the study area (states in the eastern half of the US). Exposure assessment is based on the thresholds given in Table 1 of the main text. The Jaccard index shown in Figure 7 of the main text is based on numbers in the second through fourth columns (the value in the second column divide by the sum of numbers in the second through fourth columns). Storms are ordered based on the number of counties exposed to at least one of these two exposure metrics.} 
\label{tab:misclasswind}
\begin{tabular}{cP{3cm}P{3cm}P{3cm}P{3cm}}
  \toprule
Storm & Exposed for both distance metric and wind metric & Exposed for distance metric but unexposed for wind metric & Exposed for wind metric but unexposed for distance metric & Unexposed for both distance metric and wind metric \\ 
  \midrule
Frances (2004) & 44 & 277 & 13 & 2,062 \\ 
  Cindy (2005) & 17 & 304 & 4 & 2,071 \\ 
  Dennis (2005) & 18 & 274 & 26 & 2,078 \\ 
  Ike (2008) & 166 & 67 & 82 & 2,081 \\ 
  Ivan (2004) & 29 & 255 & 27 & 2,085 \\ 
  Jeanne (2004) & 41 & 256 & 7 & 2,092 \\ 
  Allison (2001) & 21 & 266 & 0 & 2,109 \\ 
  Isidore (2002) & 29 & 239 & 7 & 2,121 \\ 
  Katrina (2005) & 66 & 175 & 32 & 2,123 \\ 
  Gordon (2000) & 11 & 244 & 6 & 2,135 \\ 
  Fay (2008) & 54 & 198 & 7 & 2,137 \\ 
  Gustav (2008) & 36 & 198 & 23 & 2,139 \\ 
  Bertha (1996) & 179 & 4 & 62 & 2,151 \\ 
  Danny (1997) & 45 & 184 & 12 & 2,155 \\ 
  Arlene (2005) & 4 & 232 & 0 & 2,160 \\ 
  Bill (2003) & 19 & 211 & 0 & 2,166 \\ 
  Dennis (1999) & 17 & 183 & 13 & 2,183 \\ 
  Hanna (2008) & 135 & 57 & 12 & 2,192 \\ 
  Isabel (2003) & 105 & 42 & 56 & 2,193 \\ 
  Ernesto (2006) & 93 & 99 & 4 & 2,200 \\ 
  Helene (2000) & 18 & 174 & 0 & 2,204 \\ 
  Rita (2005) & 26 & 139 & 20 & 2,211 \\ 
  Fran (1996) & 46 & 105 & 30 & 2,215 \\ 
  Earl (1998) & 133 & 36 & 11 & 2,216 \\ 
  Floyd (1999) & 124 & 15 & 40 & 2,217 \\ 
  Irene (2011) & 114 & 6 & 46 & 2,230 \\ 
  Lee (2011) & 34 & 110 & 0 & 2,252 \\ 
  Josephine (1996) & 62 & 61 & 3 & 2,270 \\ 
  Hermine (2010) & 22 & 101 & 1 & 2,272 \\ 
  Bonnie (2004) & 0 & 109 & 0 & 2,287 \\ 
  Frances (1998) & 15 & 47 & 0 & 2,334 \\ 
   \bottomrule
\end{tabular}
\end{table}
